---
title: "p8105_hw5_tb2715"
author: "Tess"
date: "11/5/2019"
output: github_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(viridis)
library(broom)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

# load in iris dataset
```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species)) %>%
  janitor::clean_names()
```

# Tidy Iris Database
```{r}
complete_data = function(x) {
  
   if (is.numeric(x)) {
   replace_na(x, round(mean(x, na.rm = TRUE)))
   }
   else if (is.character(x)) 
     {replace_na(x, "virginica")}
}


iris_full = map_dfr(.x = iris_with_missing, ~ complete_data(.x))

iris_full
```

In the first dataset, "iris_with_missing", there is missing petal_width for the fourth observation. After applying a function to the dataset there is now a value in its place that represents the mean of all the petal_widths. Additionally, the 22nd observation now has a species name of virginica.

## Problem 2

# Create dataset
```{r}
# create vector of file names to load using the list.files function 
file_name <- list.files(path = "./data") 

# Iterate over file names and read in data for each subject using purrr::map

import_data = function(x) {
  df = read_csv(file = str_c("./data/", x)) %>% 
    mutate(filename = x) %>% 
    separate(filename, into = c("file", "remove"), sep = "\\.") %>%
    select(-remove) %>% 
    separate(file, into = c("arm", "subject_id"), sep = "_") 
  df
}

# Run the load_data function on all file names saved in the filename_vector
combined_df = 
  tibble(file_name) %>% 
    mutate(data = map(file_name, import_data)) %>% 
      unnest()
```
## Create column titled "file name" that has subject ID and arm included ###

# clean dataset for easier interpretation
```{r}
clean_df =
combined_df %>% 
  pivot_longer(
    week_1:week_8,
      names_to = "week", 
      values_to = "observation"
  ) %>%
    mutate(arm = if_else(arm == "con", "Control", "Experimental"), 
          subject = str_replace(file_name, ".csv", "")) %>% 
   separate(week, into = c("header", "week"), sep = "_") %>%
    select(-header, -file_name) %>% 
    mutate(week = as.numeric(week))
```


# Spaghetti Plot
```{r}
clean_df %>% 
  ggplot(aes(x = week, y = observation, color = subject)) +
  geom_line() +
  labs(
    title = "Observations Across Weeks by Study Arm",
    x = "Week",
    y = "Observation Value"
  )

```
The experimental arm, as documented by the lighter color lines in the graph tends to have higher observation values over the course of the study while the control arm remains fairly flat steady. Both arms start around the same values. By week 7, all experimental values are higher than control values. 

## Question 3
```{r}
sim_regression = function(n = 30, beta0 = 2, beta1 = 0, sigma_sq = 50) {
  
  sim_data = tibble(
    x = rnorm(n),
    y = beta0 + beta1 * x + rnorm(n, 0, sigma_sq)
  )
  ls_fit = lm(y ~ x, data = sim_data) %>% 
    tidy() %>%
    select(-std.error, -statistic)}

sim_results = 
  tibble(beta1 = 0:6) %>% 
  mutate(
    output_lists = map(.x = beta1, ~rerun(10000, sim_regression(beta1 = .x))),
    estimate_dfs = map(output_lists, bind_rows)) %>% 
  select(-output_lists) %>% 
  unnest(estimate_dfs)

```

```{r}
#proportion of times null was rejected to value of B1
sim_results %>%
  group_by(beta1) %>%
  summarize(n = n(),
            prop_sig = sum(p.value < .05)/n()*100) %>%
ggplot(aes(x = beta1, y = prop_sig)) + 
  geom_point() + 
  geom_smooth(se = FALSE) + 
  labs(x = "Value of Beta1", y = "Proportion Null Rejected")
```
As the Beta1 value increases, a higher proportion of the null is rejected. This increase is seen after a Beta1 value of 2. 


```{r}
#average estimate of beta1
all_beta1 =
sim_results %>%
  mutate(average_estimate = mean(estimate)) %>%
  ggplot(aes(x = beta1, y = average_estimate)) + 
  geom_point() + 
  geom_line() + 
  labs(x = "Beta1", y = "Mean Estimate Beta1")

all_beta1

#average estimate of beta1 when null is rejected
null_beta1 = 
sim_results %>%
  filter(p.value < .05) %>%
  mutate(average_estimate = mean(estimate)) %>%
  ggplot(aes(x = beta1, y = average_estimate)) + 
  geom_point() + 
  geom_line() + 
  labs(x = "Beta1", y = "Mean Estimate Beta1 When Null Is Rejected")

null_beta1


```
THe average estimate of Beta1 compared to the true value of Beta 1 has a slope of almost 0. The mean estimate seems to match the true Beta1 value accurately. 

When the null is rejected, the average beta1 estimate is much higher than when included but it still represents the data in a 0 slope fashion that captures the true beta1 value across the range of betas. 



###### not useful code
For numeric variables, you should fill in missing values with the mean of non-missing values
For character variables, you should fill in missing values with "virginica"

iris_with_missing %>%
  summarise(mean_sepal_length = mean(sepal_length, na.rm = T))

iris_with_missing %>%
  summarise(mean_sepal_width = mean(sepal_width, na.rm = T))

iris_with_missing %>%
  summarise(mean_petal_length = mean(petal_length, na.rm = T))

iris_with_missing %>%
  summarise(mean_petal_width = mean(petal_width, na.rm = T))

## mutate data frame to replace missing values

iris_with_missing %>%
  mutate_if(sepal_length = NA, mean_sepal_length, sepal_length)

replace_missing(iris_with_missing)

{
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Z scores cannot be computed for length 1 vectors")
  }
  
##for loop

  #vector("list", 10000)
for (i in 1:10000) {
  output[[i]] = sim_regression()
}

sim_results = bind_rows(output)


names_df =
  tibble(
  subject = list.files(path="./data")
)

file_path = "./data/"

file_names = file_path %>%
  list.files()

observations_df =
  file_names %>%
  map_dfr(function(file_name){
 
  read_csv(paste0(file_path, file_name))
})

study_data = cbind(names_df, observations_df) %>%
 mutate(subject = str_replace(subject, ".csv", "")) %>%
 pivot_longer(
    week_1:week_8,
    names_to = "week",
    names_prefix = "week_",
    values_to = "observations")

